%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Unified Multi-modal Understanding and Generation for long video generation} % Topic Description
    {World Model for Long Video Generation} % Research Topic
    {Hangzhou, China} % Location
    {Dec. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of publication(s)
        \item {
        \textbf{\textit{PlasticMem}: Adding Temporal Reasoning to Diffusions for Consistent Long Video Generation} \\
        \textit{Yufei Huang}, Chao Liang, Zerong Zheng \textit{et. al}.  \space \space \space In Submission.\\
        We decompose video generation into temporal world reasoning (understanding) and independent short-video rendering (generation), unified by a diffusion-forcing objective, enabling minute-scale long video generation from short training videos only with improved data efficiency.
        }
        \item {
        \textbf{SteinsGate: Adding Causality to Diffusion for Long Video Generation via Video Path Integral} \\
        \textit{Yufei Huang} \textit{et. al}. \space \space ICLR 2026. \space \space \textit{Accepted as Poster Presentation}. \\
        We introduce temporal causality into video diffusion models by integrating temporal action binding via MLLM-based reasoning with temporal guidance, enabling coherent multi-action long video generation.
        }
      \end{cvitems}
    }
    % {Dacapo}

%---------------------------------------------------------
  \cventry
    {Integrated Guidance for few-step, high-quality, and generalizable generation.} % Topic Description
    {Modernizing Generative Models} % Research Topic
    {Hangzhou, China} % Location
    {July. 2022 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of publication(s)
        \item {
        \textbf{Improving Diffusion Generalization with Weak-to-Strong Segmented Guidance} \\
        Liangyu Yuan, \textit{Yufei Huang} \textit{et. al}.  \space \space CVPR 2026.\\
        We analyze CFG and Auto-Guidance under a unified framework, identify their optimal combinations, and propose a test-time optimization view of guidance. Thus Incorporating guidance as training or score distillation objectives to accelerate training and achieve few-step inference.
        }
        \item {
        \textbf{DaCapo: Score Distillation as Stacked Bridge for Fast and High-quality 3D Editing} \\
        \textit{Yufei Huang}, Siyuan Li, Chang Yu \textit{et. al}.  \space \space \space CVPR 2025, \space \space \textit{Accepted as Poster Presentation}.\\
        Formulating Score Distillation Sampling as Stacked Bridge and providing new insights for the speed-up of 3D-text multi-modal editing.
        }
        \item{
        \textbf{EVA: Geometric Inverse Design for fast motif-scaffolding with Coupled Flow} \\
        \textit{Yufei Huang}, Lirong Wu, Odin Zhang \textit{et. al}.  \space \space \space ICLR 2025, \space \space \textit{Accepted as Poster Presentation}.\\
        Steering flow-based models on Riemannian manifold for native part-based fast generation at inference time.
        }
        \item {
        \textbf{Re-Dock: Towards Flexible and Realistic Molecular Docking with Diffusion Bridge}\\
        \textit{Yufei Huang}, Odin Zhang, Lirong Wu \textit{et. al}. \space \space \space ICML 2024, \space \space \textit{Accepted as \textbf{Spotlight} Presentation} (Acceptance rate \textless 3.3\%).\\
        Exploring diffusion bridge model on geometric manifold (i.e., SO(3) and SO(2) group) for energy prior guided generation.
        }
        \item {
        \textbf{Protein 3D Graph Structure Learning for Robust Structure-based Protein Property Prediction}\\
        \textit{Yufei Huang}, Siyuan Li, Jin Su \textit{et.al}.  \space \space \space AAAI 2024, \space \space \textit{Accepted as Poster Presentation}.\\
        Investigating the embedding bias between synthetic and real 3D data for robust generative 3D data augmentation.
        }
      \end{cvitems}
    }
\end{cventries}
